Tropical mathematics and the Lambda-calculus I

### 2023-07-31 CSL24/section4.tex
commit

In this section we establish some topological and metric properties of such functions, this way highlighting the rich and interesting topological and metric structure of the category $\LREL_{!}$.
The literature in tropical mathematics is often recent (e.g.~\cite{Porzio2021}), and several results we prove in this section are, to our knowledge, new.

Remark that the map $(\_)^!$ is a surjective homomorphism (w.r.t.\ coKleisli composition and identity and function composition and identiy) on its image. {\color{red}In Ehrhard-Danos fanno vedere (Lemma 14) che \`e anche iniettivo. Non riesco a capire se anche a noi lo \`e, ma non vedo perch\'e non dovrebbe.}
Remark that, since $\model{(x_i:A_i)_{i=1}^n\vdash_{\STLC} M:B}\in\HOM{\LREL_!}{\mathlarger{\&}_{i=1}^n \model{A_i}}{\model B}\simeq\Lawv^{\prod_{i=1}^n ! \model {A_i}\times \model B}$, the tLs $\model{(x_i:A_i)_{i=1}^n\vdash_{\STLC} M:B}^!:\Lawv^{\mathlarger{+}_{i=1}^n \model{A_i}}\to\Lawv^{\model B} \simeq \prod_{i=1}^n\Lawv^{\model{A_i}}\to\Lawv^{\model B}$ has shape $t^!(x^1,\dots,x^n)_b=\inf_{\mu_i\in ! \model{A_i}}\left\{\sum_{i=1}^n\mu_i x^i+t_{(\mu_1,\dots,\mu_n),b}\right\}$.
Same for $\STDLC$.

\begin{remark}
The interpretations of $\BSTLC$-terms are matrices $t\in\HOM{\LREL}{\bigotimes_{i=1}^n !_{n_i}X_i}{Y}=\Lawv^{\prod_{i=1}^n !_{n_i}X_i\times Y}$.
In such situation, we define $t^!:\Lawv^{\mathlarger{+}_{i=1}^n X_{i}}\to\Lawv^Y \simeq \prod_{i=1}^n\Lawv^{X_{i}}\to\Lawv^Y$ as $t^!(x^1,\dots,x^n)_b:=\inf_{\mu_i\in !_{n_i} X_i}\left\{\sum_{i=1}^n\mu_i x^i+t_{(\mu_1,\dots,\mu_n),b}\right\}$.
Clearly $t^!={\widetilde t}^!$, where $\widetilde t\in\Lawv^{\prod_{i=1}^n ! {X_i}\times Y}$ is the matrix $\widetilde t_{(\mu_1,\dots,\mu_n),b}:=t_{(\mu_1,\dots,\mu_n),b}$ if $\mu_i\in !_{n_i} X_i$ for all $i$, and $:=\infty$ otherwise, which has the same support as $t$.
So, such $t^!$'s are special cases of tLs and thus we can \emph{Wlog} only consider tPs's.
\end{remark}

@@

% 
% , i.e.~for a \emph{finite} set $\C F\subseteq \, !X$.
%%Remark that we also find usual \emph{tropical polynomials} of tropical geometry as a particular case: they 
%correspond to the tLs for which the support $\set{n\in\N\mid\widehat f(n)\neq\infty}$ of $\widehat f$ is \emph{finite}. 
%Actually, for us \emph{tropical polynomial} will mean a function 
%\end{remark}

@@

\begin{proposition}\label{prop:nondecr+conc}
 Any tLs $f:\Lawv^X\to\Lawv^Y$ is non-decreasing and concave, w.r.t.\ the pointwise order.
\end{proposition}

%In Example~\ref{ex:famous_ex}, 
Again by looking at Fig~\ref{fig:plot1} it appears that, \emph{far from $0$}, $\varphi$ behaves like some polynomials $\varphi_{n}$.
In particular, %for all $\epsilon >0$, $f$ coincides on $[\epsilon,\infty]$ with some polynomial $\varphi_{n}$. More, precisely, 
$\varphi$ coincides on $[\epsilon,\infty]$ with $\varphi_{n}$,
for $\epsilon \geq 2^{-(n+1)}$ (the smallest tropical root of $\varphi_{n}$).
However, at
%
%$x\in [\epsilon,\infty]$, with $\epsilon>0$
%It can be proven by hand that $\varphi(x)$ is a $\min$ for all $x>0$.
 $x=0$ we have that $\varphi(x=0)=\inf_{n\in\N} 2^{-n}=0$, and this is the only point where the $\inf$ is \emph{not} a $\min$.
Also, while the derivative of $f$ is bounded on all $(0,\infty)$, for $x\to 0^+$ it tends to $\infty$.
This phenomenon is reminiscent of \cite[Example 7]{Ehrhard2005},
%Differentials and Distances in Probabilistic Coherence Spaces. FSCD 2019
which actually motivated our first investigations.
In fact, this behaviour is shared by all tLs with \emph{finitely} many variables, as shown by the following result (we identify $!\set{1,\dots,k}\simeq \N^k$, so the matrix of a tLs $f$ with finitely many variables $x=x_1,\dots,x_k$ (and one output variable) is given as a $\matr f:\N^k\to\Lawv$, $f$ having shape $f(x)=\inf_{n\in \N^k}\set{nx+\matr f(n)}$, with $nx$ the scalar product).

\begin{theorem}\label{theorem:fepsilon}
 Let $k\in\N$ and $f:\Lawv^k\to\Lawv$ a tLs with matrix $\matr f:\N^k\to\Lawv$.
 For all $0<\epsilon<\infty$, there is a \emph{finite} $\C F_\epsilon \subseteq \N^k$ such that 
% 
% \begin{enumerate}
%  \item If $\C F_\epsilon=\emptyset$ then $f=\infty$ on all $\Lawv^k$;
%  \item If $f(x_0)=\infty$ for some $x_0\in[0,\infty)^k$, then $\C F_\epsilon=\emptyset$;
  %\item 
$f$ coincides on all $[\epsilon,\infty]^k$ with the tropical \emph{polynomial} $P_\epsilon(x):=\min_{n\in \C F_\epsilon}\set{nx+\matr f(n)}$.
% \end{enumerate}
\end{theorem}
\begin{proof}[Proof sketch]
Let $\C F_\epsilon$ be the set of $n\in\N^{k}$ such that 
$\widehat f(n)<\infty$ and $\widehat f(m)> \widehat f(n)+\epsilon$ holds for all $m\prec n$, where $\preceq$ is the pointwise order on $\N^k$.
The core of the proof is showing that this set is indeed finite and enough for computing $f$.
\end{proof}

In all the remainder of this section we consider the sets $\Lawv^X$ endowed with the usual sup-norm $\norm{x}_\infty:=\sup_{a\in X} x_a$.

\subparagraph*{Continuity of tLs}\label{subsec:cont}%$\Lawv^{X}$ as a normed cone}

The tLs $\varphi$ is continuous on $\BB R_{\geq0}$ (w.r.t.\ the usual norm of real numbers).
We can generalise this property, dropping the case of $x$ having some $0$ coordinate.
But we have to be careful, because while in the finite dimensional $\BB R^n$, every real convex function is continuous because it is necessarily locally bounded from above (the sup-norm and the euclidean one are equivalent) \cite[Proposition 4.7]{Cobzas2017}, in infinite dimensions the former condition is no longer true \cite[Example 4.8]{Cobzas2017}.
However, \cite[Proposition 4.4.(3)]{Cobzas2017} shows that it is the only requirement to ask: if a real-valued convex function with domain a convex open subset of a locally convex topological $\BB R$-vector space (LCTVS) is, locally around any point, bounded from above by a finite non-zero constant, then it is continuous on all its domain.

\begin{theorem}\label{thm:cont}
 All tLs $f:\Lawv^X\to\Lawv$ are continuous on $(0,\infty)^X$, w.r.t.\ to the norm $\norm{\cdot}_\infty$.
\end{theorem}
\begin{proof}
%It follows after adapting \cite[Proposition 4.4]{Cobzas2017} in order to prove that if a real-valued function on a locally convex topological $\BB R$-vector space is, locally around $x$, concave and bounded by a finite constant, then it is continuous at $x$.
%Now, our $f$ is concave, so 
By \autoref{prop:nondecr+conc}, $-f$ is convex.
Since $f\geq 0$ on all $\Lawv^X$, we have e.g.\ $-f\leq 1$ on $\Lawv^X$.
%Remark that we cannot immediately apply \cite[Proposition 4.4.(3)]{Cobzas2017}, since $\Lawv^X$ is not even a $\BB R$-vector space.
Now $(0,\infty)^X\subseteq \BB R^X$ is open and convex, and {\color{red}$\BB R^X$ is a LCTVS}, so \cite[Proposition 4.4.(3)]{Cobzas2017} entails the continuity of $-f\big|_{(0,\infty)^X}$, hence that of $f\big|_{(0,\infty)^X}$.
\end{proof}

@@

\begin{theorem}\label{thm:ScottCont}
 All monotone (w.r.t.\ pointwise order) and $\norm{\cdot}_{\infty}$-continuous functions $f:(0,\infty)^X\to (0,\infty)$ are Scott-continuous.
 In particular, all tLs $f:\Lawv^X\to\Lawv$ are Scott-continuous on $(0,\infty)^X$ w.r.t.\ the pointwise orders.
\end{theorem}
\begin{proof}
 Uses \autoref{thm:cont} plus the fact, taken from \cite{Selinger2004}, that in a normed $\R_{\geq 0}$-cone $P$, considered with its cone-order, if every bounded directed net in $P$ admits a sup, and if $(v_i)_{i\in I}$ is a directed net in $P$ with an upper bound $v\in P$, then $\exists\bigvee_{i\in I} v_i \in P$ and, if $\inf_{i\in I} \norm{v-v_i} =0$, one has $\bigvee_{i\in I} v_i = v$.
\end{proof}

\subparagraph*{Lipschitz-continuity of tLs}\label{sec:4C}%$\Lawv^{X}$ as a metric space.}

%The norm $\norm{\cdot}_\infty$ naturally induces a metric $\norm{x-y}_{\infty}$ over the spaces $\Lawv^{X}$.
%We will show that tLs satisfy suitable Lipschitz properties w.r.t.\ $\norm{\cdot}_\infty$.

Let us first look at tropical linear functions:
in analogy with that happens in usual metric semantics, we have:

\begin{proposition}\label{prop:troplinear}
All tropical \emph{linear} functions $f: \Lawv^{X}\to \Lawv^{Y}$ are non-expansive (i.e.\ $1$-Lipschitz).  
\end{proposition}
%\begin{proof}[Proof sketch]
%Using the fact that $f(\B x)_{b}= \inf_{a\in X}\matr f_{a,b}+\B x_{a}$,
%the problem reduces to checking that $|(\matr f_{a,b}-\B x_{a})- (\matr f_{a,b}-\B y_{a})| = |\B x_{a}-\B y_{a}|\leq \| \B x-\B y\|_{\infty}$.\end{proof} 
%\begin{proof}
%Using $f(\B x)_{b}= \inf_{a\in X}\matr f_{a,b}+\B x_{a}$,
%first observe that $|(\matr f_{a,b}-\B x_{a})- (\matr f_{a,b}-\B y_{a})| = |\B x_{a}-\B y_{a}|\leq \| \B x-\B y\|_{\infty}$; we now have
%$|f(\B x)_{b}-f(\B y)_{b}| \leq |(\inf_{a\in X}\matr f_{a,b}-\B x_{a})-(\inf_{a\in X}\matr f_{a,b}-\B y_{a})| \leq
%\sup_{a\in X}|(\matr f_{a,b}-\B x_{a})- (\matr f_{a,b}-\B y_{a})|\leq 
% \| \B x-\B y\|_{\infty}$.
%\end{proof}

@@

Let us now consider the case of bounded exponentials:
\begin{proposition}\label{prop:boundedlip}
If a tLs $f: \Lawv^{X}\to \Lawv^{Y}$ arises from a matrix $\matr f:!_{n}X\times Y\to \Lawv$, then $f$ is $n$-Lipschitz-continuous.
\end{proposition}
\begin{proof}[Proof sketch]
This follows from Proposition \ref{prop:troplinear} and the remark that, for all $x\in \Lawv^{X}$, $\norm{ !_{n} x-!_{n} y}_{\infty}\leq n\cdot \norm{ x- y}_{\infty}$, where $!_{n} x$ is the restriction of $! x$ to $\C M_{\leq n}(X)$.%
%Using the fact that $f(\B x)_{b}=\inf_{\mu\in \C M_{\leq n}(X)}\{ \matr f_{\mu,b}+ \mu (!_{n}\B x) \}$, where $!_{n}\B x\in \Lawv^{\C M_{\leq n}(X)}$ is given by 
%$(!_{n}\B x)_{[a_{1},\dots, a_{k}]}=\sum_{i=1}^{k}\B x_{a_{i}}$, 
%it suffices to check that $\| (!_{n}\B x)-(!_{n}\B y)\|_{\infty}\leq n\cdot \| \B x-\B y\|_{\infty}$ and apply Proposition \ref{prop:troplinear}.
\end{proof}
This result is perfectly analogous to what happens in the metric models discussed in Section \ref{section2}, the bounded exponentials $!_{n}$ playing the role of the re-scaling trick.

Observe that, for any tropical polynomial $\varphi:\Lawv^{X}\to \Lawv^{Y}$, the associated matrix has shape $!_{\mathrm{deg}(\varphi)}(X)\times Y\to \Lawv$ (as a monomial $\mu_ix+c_{i}$ yields a matrix entry on $!_{\#\mu_i}X\times Y$). Hence, using Proposition \ref{prop:boundedlip}, we have:
\begin{corollary}\label{prop:polylip}
For any tropical polynomial $\varphi:\Lawv^{X}\to\Lawv$, $\varphi$ is $\mathrm{deg}(\varphi)$-Lipschitz continuous.
\end{corollary}

Let us now look at what happens with tLs, i.e.~when considering the full exponential $!$.
As consequence of Theorem~\ref{theorem:fepsilon}, the tLs with \emph{finitely many} variables are always \emph{locally} Lipschitz on all $(0,\infty)^X$.
%Actually, we can prove a more general statement, also covering the infinitary case.

We wish now to move to the case of infinitely many variables.
In \cite[Theorem 6.4]{Cobzas2017} a locally Lipschitz property is obtained for locally convex topological vector spaces, under the hypothesis of continuity. \cite[Proposition 6.5]{Cobzas2017} shows that continuity is used in order to have a locally bounded condition, the true main ingredient of the proof.
Instead of showing how our case fits into such theorems, we prefer to state a theorem, which is basically a particular case of \cite[Theorem 6.9, Lemma 6.10]{Cobzas2017}, already fitting in the topics under consideration in this paper.

\begin{theorem}\label{thmTLSlocLip}
 Let $f:V\subseteq (\BB R^X,d) \to (\BB R,\absv \cdot)$, with $V$ open and convex and $d$ any metric.
 If $f$ is concave and locally bounded, then $f$ is locally Lipschitz.
 Moreover, the Lipschitz constant of $f$ on $\overline{B_{\delta}(x)}$ can be chosen to be $\frac{1}{\delta}\max_{\overline{B_{3\delta}(x)}} \absv f$.

Therefore, since $(0,\infty)^X$ is open and convex in $(\BB R^X,\norm\cdot)$, %and all tLs are non-negative, 
we immediately have that all tLs $f:\Lawv^X\to\Lawv$ are locally Lipschitz on $(0,\infty)^X$.
Moreover, the Lipschitz constant of $f$ on $\overline{B_{\delta}(x)}$ can be chosen to be $\frac{1}{\delta}\max_{\overline{B_{3\delta}(x)}} f$.
\end{theorem}
%\begin{proof}[Proof]
% Call $\overline{B_{\delta}(x)}:=B_1$, $\overline{B_{3\delta}(x)}:=B_3$.
% It suffices to show that for all $x\in V$, there is $\delta>0$ s.t.\ $B_3\subseteq \mathrm{interior}(V)$, $K:=\max_{B_3}  \absv f$ exists and $f_{\big|_{B_1}}$ is $(\frac{1}{\delta}\max_{B_3} \absv f)$-Lipschitz.
%A $\delta$ satisfying the first two conditions exists since $V$ is open and bcause $f$ is locally bounded and $B_3$ is compact.
%Now fix $y,z\in B_1$.
%Call $r:=\frac{d(y,z)}{2\delta}\in[0,1]$.
%We have to show that $\absv{f(y)-f(z)}\leq \frac{K}{\delta}d(y,z)=2Kr$.
%Wlog $y\neq z$.
%So $r\neq 0$ and we can consider $u:=\frac{1+r}{r}z-\frac{1}{r}y$, $v:=\frac{1}{r}y-\frac{r-1}{r}z$.
%We have $u,v\in \overline{B_{2\delta}(z)}=:B_2$ (geometrically, those are the intersections between $B_2$ and the segment between $y$ and $z$).
%Now we have the convex combinations $z=\frac{1}{1+r}y+\frac{r}{1+r}u$ and $y=(1-r)z+rv$, so the concavity of $f$ entails on one hand:
%$f(z)\geq \frac{1}{1+r}f(y)+\frac{r}{1+r}f(z)\geq \frac{f(y)}{1+r} - \frac{rK}{1+r}$, i.e.\ $f(y)-f(z)\leq r(K+f(z))\leq 2rK$, and on the other hand:
%$f(y)\geq (1-r)f(z)+rf(v)\geq f(z)-r(f(z)+K)$, i.e.\ $f(z)-f(y)\leq r(f(z)+K)\leq 2rK$.
%The last inequalities follow because $B_2\subseteq B_3$.
%Putting those together, we have the thesis.
%\end{proof}

\subparagraph*{Tropical differential of tLs}

>>>>

% !TEX root = /Users/paolopistone/Documents/GitHub/tropicalnew/CSL24/main.tex

In this section we establish some topological and metric properties of tps, this way highlighting the rich and interesting topological and metric structure of the category $\LREL_{!}$.
The literature in tropical mathematics is often recent (e.g.~\cite{Porzio2021}), and several results we prove in this section are, to our knowledge, new.
%
%Remark that the map $(\_)^!$ is a surjective homomorphism (w.r.t.\ coKleisli composition and identity and function composition and identiy) on its image. {\color{red}In Ehrhard-Danos fanno vedere (Lemma 14) che \`e anche iniettivo. Non riesco a capire se anche a noi lo \`e, ma non vedo perch\'e non dovrebbe.}
%Remark that, since $\model{(x_i:A_i)_{i=1}^n\vdash_{\STLC} M:B}\in\HOM{\LREL_!}{\mathlarger{\&}_{i=1}^n \model{A_i}}{\model B}\simeq\Lawv^{\prod_{i=1}^n ! \model {A_i}\times \model B}$, the tps $\model{(x_i:A_i)_{i=1}^n\vdash_{\STLC} M:B}^!:\Lawv^{\mathlarger{+}_{i=1}^n \model{A_i}}\to\Lawv^{\model B} \simeq \prod_{i=1}^n\Lawv^{\model{A_i}}\to\Lawv^{\model B}$ has shape $t^!(x^1,\dots,x^n)_b=\inf_{\mu_i\in ! \model{A_i}}\left\{\sum_{i=1}^n\mu_i x^i+t_{(\mu_1,\dots,\mu_n),b}\right\}$.
%Same for $\STDLC$.
%
%\begin{remark}
%The interpretations of $\BSTLC$-terms are matrices $t\in\HOM{\LREL}{\bigotimes_{i=1}^n !_{n_i}X_i}{Y}=\Lawv^{\prod_{i=1}^n !_{n_i}X_i\times Y}$.
%In such situation, we define $t^!:\Lawv^{\mathlarger{+}_{i=1}^n X_{i}}\to\Lawv^Y \simeq \prod_{i=1}^n\Lawv^{X_{i}}\to\Lawv^Y$ as $t^!(x^1,\dots,x^n)_b:=\inf_{\mu_i\in !_{n_i} X_i}\left\{\sum_{i=1}^n\mu_i x^i+t_{(\mu_1,\dots,\mu_n),b}\right\}$.
%Clearly $t^!={\widetilde t}^!$, where $\widetilde t\in\Lawv^{\prod_{i=1}^n ! {X_i}\times Y}$ is the matrix $\widetilde t_{(\mu_1,\dots,\mu_n),b}:=t_{(\mu_1,\dots,\mu_n),b}$ if $\mu_i\in !_{n_i} X_i$ for all $i$, and $:=\infty$ otherwise, which has the same support as $t$.
%So, such $t^!$'s are special cases of tps and thus we can \emph{Wlog} only consider tps's.
%\end{remark}

@@

% 
% , i.e.~for a \emph{finite} set $\C F\subseteq \, !X$.
%%Remark that we also find usual \emph{tropical polynomials} of tropical geometry as a particular case: they 
%correspond to the tps for which the support $\set{n\in\N\mid\widehat f(n)\neq\infty}$ of $\widehat f$ is \emph{finite}. 
%Actually, for us \emph{tropical polynomial} will mean a function 
%\end{remark}

%
%%In Example~\ref{ex:famous_ex}, 
%Again by looking at Fig~\ref{fig:plot1} it appears that, \emph{far from $0$}, $\varphi$ behaves like some polynomials $\varphi_{n}$.
%In particular, %for all $\epsilon >0$, $f$ coincides on $[\epsilon,\infty]$ with some polynomial $\varphi_{n}$. More, precisely, 
%$\varphi$ coincides on $[\epsilon,\infty]$ with $\varphi_{n}$,
%for $\epsilon \geq 2^{-(n+1)}$ (the smallest tropical root of $\varphi_{n}$).
%However, at
%%
%%$x\in [\epsilon,\infty]$, with $\epsilon>0$
%%It can be proven by hand that $\varphi(x)$ is a $\min$ for all $x>0$.
% $x=0$ we have that $\varphi(x=0)=\inf_{n\in\N} 2^{-n}=0$, and this is the only point where the $\inf$ is \emph{not} a $\min$.
%Also, while the derivative of $f$ is bounded on all $(0,\infty)$, for $x\to 0^+$ it tends to $\infty$.
%This phenomenon is reminiscent of \cite[Example 7]{Ehrhard2005},
%%Differentials and Distances in Probabilistic Coherence Spaces. FSCD 2019
%which actually motivated our first investigations.
%In fact, this behaviour is shared by all tps with \emph{finitely} many variables, as shown by the following result (we identify $!\set{1,\dots,k}\simeq \N^k$, so the matrix of a tps $f$ with finitely many variables $x=x_1,\dots,x_k$ (and one output variable) is given as a $\matr f:\N^k\to\Lawv$, $f$ having shape $f(x)=\inf_{n\in \N^k}\set{nx+\matr f(n)}$, with $nx$ the scalar product).
%
%\begin{theorem}\label{theorem:fepsilon}
% Let $k\in\N$ and $f:\Lawv^k\to\Lawv$ a tps with matrix $\matr f:\N^k\to\Lawv$.
% For all $0<\epsilon<\infty$, there is a \emph{finite} $\C F_\epsilon \subseteq \N^k$ such that 
%% 
%% \begin{enumerate}
%%  \item If $\C F_\epsilon=\emptyset$ then $f=\infty$ on all $\Lawv^k$;
%%  \item If $f(x_0)=\infty$ for some $x_0\in[0,\infty)^k$, then $\C F_\epsilon=\emptyset$;
%  %\item 
%$f$ coincides on all $[\epsilon,\infty]^k$ with the tropical \emph{polynomial} $P_\epsilon(x):=\min_{n\in \C F_\epsilon}\set{nx+\matr f(n)}$.
%% \end{enumerate}
%\end{theorem}
%\begin{proof}[Proof sketch]
%Let $\C F_\epsilon$ be the set of $n\in\N^{k}$ such that 
%$\widehat f(n)<\infty$ and $\widehat f(m)> \widehat f(n)+\epsilon$ holds for all $m\prec n$, where $\preceq$ is the pointwise order on $\N^k$.
%The core of the proof is showing that this set is indeed finite and enough for computing $f$.
%\end{proof}
%
In all the remainder of this section we consider the sets $\Lawv^X$ endowed with the usual sup-norm $\norm{x}_\infty:=\sup_{a\in X} x_a$.

\subparagraph*{Continuity of tps}\label{subsec:cont}%$\Lawv^{X}$ as a normed cone}

@@

\begin{proposition}\label{prop:nondecr+conc}
 All tps 
 %$f:\Lawv^X\to\Lawv^Y$
are non-decreasing and concave, w.r.t.\ the pointwise order on $\Lawv^{X}$.
\end{proposition}

The tps $\varphi$ is continuous on $\BB R_{\geq0}$ (w.r.t.\ the usual norm of real numbers).
We can generalise this property, dropping the case of $x$ having some $0$ coordinate.
But we have to be careful, because while in the finite dimensional $\BB R^n$, every real convex function is continuous because it is necessarily locally bounded from above (the sup-norm and the euclidean one are equivalent) \cite[Proposition 4.7]{Cobzas2017}, in infinite dimensions the former condition is no longer true \cite[Example 4.8]{Cobzas2017}.
However, \cite[Proposition 4.4.(3)]{Cobzas2017} shows that it is the only requirement to ask: if a real-valued convex function with domain a convex open subset of a locally convex topological $\BB R$-vector space (LCTVS) is, locally around any point, bounded from above by a finite non-zero constant, then it is continuous on all its domain.

\begin{theorem}\label{thm:cont}
 All tps $f:\Lawv^X\to\Lawv$ are continuous on $(0,\infty)^X$, w.r.t.\ to the norm $\norm{\cdot}_\infty$.
\end{theorem}
\begin{proof}
%It follows after adapting \cite[Proposition 4.4]{Cobzas2017} in order to prove that if a real-valued function on a locally convex topological $\BB R$-vector space is, locally around $x$, concave and bounded by a finite constant, then it is continuous at $x$.
%Now, our $f$ is concave, so 
By \autoref{prop:nondecr+conc}, $-f$ is convex.
Since $f\geq 0$ on all $\Lawv^X$, we have e.g.\ $-f\leq 1$ on $\Lawv^X$.
%Remark that we cannot immediately apply \cite[Proposition 4.4.(3)]{Cobzas2017}, since $\Lawv^X$ is not even a $\BB R$-vector space.
Now $(0,\infty)^X\subseteq \BB R^X$ is open and convex, and {\color{red}$\BB R^X$ is a LCTVS}, so \cite[Proposition 4.4.(3)]{Cobzas2017} entails the continuity of $-f\big|_{(0,\infty)^X}$, hence that of $f\big|_{(0,\infty)^X}$.
\end{proof}

@@

\begin{theorem}\label{thm:ScottCont}
 All monotone (w.r.t.\ pointwise order) and $\norm{\cdot}_{\infty}$-continuous functions $f:(0,\infty)^X\to (0,\infty)$ are Scott-continuous.
 In particular, all tps $f:\Lawv^X\to\Lawv$ are Scott-continuous on $(0,\infty)^X$ w.r.t.\ the pointwise orders.
\end{theorem}
\begin{proof}
 Uses \autoref{thm:cont} plus the fact, taken from \cite{Selinger2004}, that in a normed $\R_{\geq 0}$-cone $P$, considered with its cone-order, if every bounded directed net in $P$ admits a sup, and if $(v_i)_{i\in I}$ is a directed net in $P$ with an upper bound $v\in P$, then $\exists\bigvee_{i\in I} v_i \in P$ and, if $\inf_{i\in I} \norm{v-v_i} =0$, one has $\bigvee_{i\in I} v_i = v$.
\end{proof}

\subparagraph*{Lipschitz-continuity of tps}\label{sec:4C}%$\Lawv^{X}$ as a metric space.}

%The norm $\norm{\cdot}_\infty$ naturally induces a metric $\norm{x-y}_{\infty}$ over the spaces $\Lawv^{X}$.
%We will show that tps satisfy suitable Lipschitz properties w.r.t.\ $\norm{\cdot}_\infty$.

Let us first look at what happens with those tps which are either \emph{linear} or obtained via bounded exponentials.
The result below is in analogy with that happens in the usual metric semantics of Fuzz, where 
linear functions are non-expansive and $n$-bounded functions are $n$-Lipschitz \cite{Reed2010}.

\begin{proposition}\label{prop:troplinear}
\begin{enumerate}
\item If a tps $f: \Lawv^{X}\to \Lawv^{Y}$ arises from a matrix $\matr f:X\times Y\to \Lawv$ (i.e.~it is linear), then $f$ is non-expansive (i.e.\ $1$-Lipschitz).  
\item If  $f \Lawv^{X}\to \Lawv^{Y}$ arises from a matrix $\matr f: \ !_{n}X\times Y\to \Lawv$, then $f$ is $n$-Lipschitz-continuous.
\end{enumerate}
\end{proposition}
\begin{proof}[Proof sketch]
1). Using the fact that $f( x)_{b}= \inf_{a\in X}\{\matr f_{a,b}+ x_{a}\}$,
the problem reduces to checking that $|(\matr f_{a,b}- x_{a})- (\matr f_{a,b}- y_{a})| = |x_{a}- y_{a}|\leq \|  x- y\|_{\infty}$.

2.) Follows from 1.~and the remark that, for all $x\in \Lawv^{X}$, $\norm{ !_{n} x-!_{n} y}_{\infty}\leq n\cdot \norm{ x- y}_{\infty}$, where $!_{n} x$ is the restriction of $! x$ to $\C M_{\leq n}(X)$.%
\end{proof} 
%\begin{proof}
%Using $f(\B x)_{b}= \inf_{a\in X}\matr f_{a,b}+\B x_{a}$,
%first observe that $|(\matr f_{a,b}-\B x_{a})- (\matr f_{a,b}-\B y_{a})| = |\B x_{a}-\B y_{a}|\leq \| \B x-\B y\|_{\infty}$; we now have
%$|f(\B x)_{b}-f(\B y)_{b}| \leq |(\inf_{a\in X}\matr f_{a,b}-\B x_{a})-(\inf_{a\in X}\matr f_{a,b}-\B y_{a})| \leq
%\sup_{a\in X}|(\matr f_{a,b}-\B x_{a})- (\matr f_{a,b}-\B y_{a})|\leq 
% \| \B x-\B y\|_{\infty}$.
%\end{proof}

@@

%Let us now consider the case of bounded exponentials:
%\begin{proposition}\label{prop:boundedlip}
%If a tps $f: \Lawv^{X}\to \Lawv^{Y}$ arises from a matrix $\matr f:!_{n}X\times Y\to \Lawv$, then $f$ is $n$-Lipschitz-continuous.
%\end{proposition}
%\begin{proof}[Proof sketch]
%This follows from Proposition \ref{prop:troplinear} and the remark that, for all $x\in \Lawv^{X}$, $\norm{ !_{n} x-!_{n} y}_{\infty}\leq n\cdot \norm{ x- y}_{\infty}$, where $!_{n} x$ is the restriction of $! x$ to $\C M_{\leq n}(X)$.%
%%Using the fact that $f(\B x)_{b}=\inf_{\mu\in \C M_{\leq n}(X)}\{ \matr f_{\mu,b}+ \mu (!_{n}\B x) \}$, where $!_{n}\B x\in \Lawv^{\C M_{\leq n}(X)}$ is given by 
%%$(!_{n}\B x)_{[a_{1},\dots, a_{k}]}=\sum_{i=1}^{k}\B x_{a_{i}}$, 
%%it suffices to check that $\| (!_{n}\B x)-(!_{n}\B y)\|_{\infty}\leq n\cdot \| \B x-\B y\|_{\infty}$ and apply Proposition \ref{prop:troplinear}.
%\end{proof}
%This result is perfectly analogous to what happens in the metric models discussed in Section \ref{section2}, the bounded exponentials $!_{n}$ playing the role of the re-scaling trick.

Observe that, for any tropical polynomial $\varphi:\Lawv^{X}\to \Lawv^{Y}$, the associated matrix has shape $!_{\mathrm{deg}(\varphi)}(X)\times Y\to \Lawv$ (as a monomial $\mu_ix+c_{i}$ yields a matrix entry on $!_{\#\mu_i}X\times Y$). Hence, using Proposition \ref{prop:troplinear} 2., we have:
\begin{corollary}\label{prop:polylip}
For any tropical polynomial $\varphi:\Lawv^{X}\to\Lawv$, $\varphi$ is $\mathrm{deg}(\varphi)$-Lipschitz continuous.
\end{corollary}

Let us now look at what happens with tps, i.e.~when considering the full exponential $!$.
First observe that, as consequence of Theorem~\ref{theorem:fepsilon}, the tps with \emph{finitely many} variables are always \emph{locally} Lipschitz on all $(0,\infty)^X$. Yet, for the case of infinitely many variables we need a more general argument.
In \cite[Theorem 6.4]{Cobzas2017} a locally Lipschitz property is obtained for locally convex topological vector spaces, under the hypothesis of continuity. \cite[Proposition 6.5]{Cobzas2017} shows that continuity is used in order to have a locally bounded condition, the true main ingredient of the proof.
Instead of showing how our case fits into such theorems, we prefer to state a theorem, which is basically a particular case of \cite[Theorem 6.9, Lemma 6.10]{Cobzas2017}:
%, already fitting in the topics under consideration in this paper.
